Seasonality in governing upper-ocean dynamics at submesoscales

### 2016-06-06 writeup/rocha_etal.tex
Updates figures and bib
Fixes legends

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.9\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  horizontal divergence (b) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig3.pdf}
 \caption{Surface (horizontal) KE and SSH variance wavenumber spectra. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig3}
 \end{center}
\end{figure*}

>>>>

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.9\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  lateral rate of strain (b), and horizontal divergence (c) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions: vorticity vs.
          divergence (a through e) and vorticity vs. strain rate (f through j).
          Dashed lines in (a) through (e) represent $\delta = \frac{\omega}{f_0}
          \zeta$ where $\omega = 2\pi/$(12 h, 3 h) and $f_0$ is the inertial frequency
          in the middle of the domain (32.5$^\circ$ N). Dashed lines in (f) through (j)
          represent pure strain flow $\alpha = \zeta$.}
 \label{fig3}
 \end{center}
\end{figure*}

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig3}
 \end{center}
\end{figure*}
